---
title: "linear model"
author: "David Taylor"
date: "27/11/2018"
output: html_document
---

**Demonstrates simulating a linear model with some noise**

```{r}
set.seed(30) # for reproduceability
x <- rnorm(100) # take 100 randomn samples from a normal distribution mean 0 sd 1 
e <- rnorm(100,0,0.5) # and simulate some noise 
y <- 4.5 + 2*x + e # Creates data set intercept 4.5, gradient 2.0 add noise
```

So now we have a data set 'y' simulating a linear relationship with x with added noise.
This can be output from base 'R' as shown:

```{r, echo=FALSE}
plot(x,y)
```

Now we run a linear model (z) of y as a function of x

```{r}
z <- lm(y ~ x) 
plot(x,y) # replot the variables
abline(z$coefficients) # add a line to plot to show the model's trendline
```

So, despite our 'true' disctibution having an intercept of 4.5 and a slope of 2 
we can see that the noise element has intruduced an error into the model:

```{r}
z$coefficients
```

For completeness lets take a look at the structure of the model: 

```{r}
str(z) # shows us what R has in the model
```